Workflow Part II: Inverse root modeling and post-processing

### 2021-02-22 Readme.Rmd
reorganised

Script to load data generated from the data preparation script above for use in inverse model as well as manuscript. It's needed for rest of the scripts.

@@

**Figures**

```{r Chunk 08.0, eval = FALSE}
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
```

**Main text**

```{r Chunk 09.0, eval = FALSE}
render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
```

>>>>

Script to load data generated from the data preparation script above for use in inverse model as well as manuscript. It's used within the rest of the scripts.

@@

**Main text**
```{r Chunk 09.0, eval = FALSE}
# Two files are used within the report
# For data, 06.0_load.R and 
# For figures and data, code/08.0_manuscript_data_figs.R
groundhog.day = "2020-05-01"
groundhog.library('rmarkdown', groundhog.day)
groundhog.library('bookdown', groundhog.day)
rmarkdown::render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
```
